Scaling of Electrode-Electrolyte Interface Model Parameters In Phosphate Buffered Saline

### 2014-06-25 paper.tex
Added two new references from TBioCas as requested

\IEEEPARstart{T}{here} is considerable interest in the electrical modelling of electrodes. \cite{Cogan2008,Troy2006}
In \cite{Franks2005} a linearised model was presented, and in \cite{ScottSingle2013} a non-linear model
suitable for use with the SPICE circuit simulator was presented. The SPICE model usefully characterises an electrode in a given electrolyte with a small number of parameters.
One major reason for the interest in the electrical impedance of electrodes concerns the design of electronics intended for integration into pacemakers, cochlear implants, spinal cord stimulators, etc. The design of successful circuits depends upon a good understanding of external load impedance, while maximisation of battery life is linked to the use of electrodes whose impedance is well understood.

@@

>>>>

\IEEEPARstart{T}{here} is considerable interest in the electrical modelling of electrodes. \cite{Cogan2008,Brown2008,Guo2012,Troy2006}
In \cite{Franks2005} a linearised model was presented, and in \cite{ScottSingle2013} a non-linear model
suitable for use with the SPICE circuit simulator was presented. The SPICE model usefully characterises an electrode in a given electrolyte with a small number of parameters.
One major reason for the interest in the electrical impedance of electrodes concerns the design of electronics intended for integration into pacemakers, cochlear implants, spinal cord stimulators, etc. The design of successful circuits depends upon a good understanding of external load impedance, while maximisation of battery life is linked to the use of electrodes whose impedance is well understood.

@@

\bibitem{Brown2008}
    Edgar~A.~Brown, James~D.~Ross, Richard~A.~Blum, Yoonkey~Nam, Bruce~C.~Wheeler and Stephen~P.~DeWeerth,
    ``Stimulus-Artifact Elimination in a Multi-Electrode System'',
    {\em IEEE Transactions on Biomedical Circuits and Systems},
    vol.~2 no.~1, March 2008, pp10--21.

\bibitem{Guo2012}
    Jing~Guo, Jie~Yuan and Mansun~Chan,
    {\em IEEE Transactions on Biomedical Circuits and Systems},
    vol.~6 no.~6, December 2012, pp605--613.
